\section{Systematics}
\subsection{Nuclear Dependence of $R=\sigma_L/\sigma_T$}


Due to the relatively low energy of the 6~GeV JLab E03-103 measurements, effects due to acceleration and
deceleration of electrons in the Coulomb field of the heavier targets (Cu and Au) could not be ignored.
However, once applied, these so-called Coulomb corrections resulted in ratios systematically larger
than those found by previous experiments.  This apparent discrepancy motivated the re-examination of
earlier measurements, and it was found that, while the bulk of the large $x$ measurements from SLAC
were taken at significantly higher beam energies, SLAC E140 (an experiment dedicated to studying
the nuclear dependence of $R=\sigma_L/\sigma_T$) had used beam energies similar to JLab E03-103, but for
those measurements had not applied Coulomb corrections.  Once Coulomb corrections were applied to the E140
results, the conclusion that there was no evidence for a nuclear dependence of $R$ was less strong, with
$\Delta R=R_A-R_D$ about 1.5 standard deviations from zero. Further, when a combined analysis
of available SLAC E139, E140, and JLab E03-103 data was performed for data at $x=0.5$ and $Q^2\approx5$~GeV$^2$,
a similar deviation of $\Delta R$ was found~\cite{Solvignon:2009it}.

This result, combined with hints of a difference in $R$ for protons and deuterium motivated a 
new experiment to make further measurements of the nuclear dependence of $R=\sigma_L/\sigma_T$
with better precision than E140 and for a wider range of $x$ and $Q^2$ than previously
measured~\cite{12gev_nucr}.  This experiment will provide precise measurements of $R=\sigma_L/\sigma_T$
for the nucleon for $0.1<x<0.6$ and $1<Q^2<5~\text{GeV}^2$ as well as determination of $\Delta R= R_A-R_d$ for the same
kinematics using a copper target. Additional data will also be taken with carbon and gold targets for a subset
of the kinematics.


\subsection{Hadronization and Final State Effects}

Another aspect that would be beneficial for the extraction of the nPDFs is the improvement of our understanding of final state effects. Unlike proton PDFs, where the determination of the gluon is not contaminated by final states, the nPDFs have been including routinely particle production in $d+\mathrm{Au}$ collisions into the fits, an observable that is very sensitive to both the initial and final state (hadronization) of the gluon. This would be in principle a perfectly adequate idea, except that it has some caveats. The fragmentation functions (FFs) in the vacuum are best determined for the pions, with the gluon fragmentation having a sizable theoretical uncertainty. Moreover data from the LHC at $7$ GeV can not be well described by a global fit unless a significant cut in $p_{T}$ is applied to the date, leaving out a relevant portion of the $d+Au$ covered region. Furthermore, when it comes to particle production in a nuclear medium it is yet unclear how much of the measured effects can be attributed to the nPDFs and how much of it, if any, is a final state effect due to the partons interacting with the medium before the hadronization. The only semi-inclusive DIS off nuclei, measured at HERMES, shows a significant effect that has yet to be understood. This constitutes a sizable source of uncertainty for the extraction of the nPDFs and therefore conclusions from incorporating particle production data form RHIC into the fits must be drawn carefully.


\subsection{Free Nucleon Parton Distributions}

While the free proton parton distributions have been studied extensively and with great precision, there still remain important measurements to be done to constrain the two leading-flavor parton distributions, in particular in the ratio of $d/u$ limit as $x \rightarrow 1$.  As these represent the basis of comparison for any nuclear modification effect, it is critical to have high quality data available, especially as one considers doing flavor decompositions of nuclei.  There are several programs which intend to improve the fixed-target lepton scattering data, such as using the ratio of ${}^{3}$H and ${}^{3}$He cross section~\cite{mar}, tagged spectator with deuterium~\cite{bonus12}, and parity-violating deep inelastic scattering on the proton~\cite{solid_pvdis}.  In addition, recent analyses of $W$ and $Z$ production in $p\bar{p}$ collisions from the CDF and D\O\ collaborations~\cite{D0:2014kma,Abazov:2013dsa,Acosta:2005ud,Aaltonen:2009ta,Aaltonen:2010zza,Abazov:2007jy} have also provided new constraints at large $x$ and have been incorporated into a recent global PDF analysis~\cite{Accardi:2016qay}.

